Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-06 contents/implementation.tex

\begin{figure}[b!]
    \centering
    \includegraphics[width=0.4\textwidth]{resources/svs2}
    \caption{Exemplar SVS shape representation. A similar SVS image is obtained from different annotations of the same shape.}
    \label{fig:build_svs}
\end{figure}

@@

\begin{figure}[t!]
        \centering
        \begin{tabular}{ccc}
        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/1}
        &
        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/2}
        &
        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/3}
        \\
        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/4}
        &
        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/5}
        &
        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/6}
        \end{tabular}
    \caption{Exemplar deformation fields for the left forearm, obtained using the proposed pipeline. Figure best viewed by zooming in.}
    \label{fig:deformationfield}
\end{figure}

>>>>

% \begin{figure}[b!]
%     \centering
%     \includegraphics[width=0.4\textwidth]{resources/svs2}
%     \caption{Exemplar SVS shape representation. A similar SVS image is obtained from different annotations of the same shape.}
%     \label{fig:build_svs}
% \end{figure}

@@

\begin{figure}[t!]
    \centering
    \newcommand{\flowh}{0.25\columnwidth}
    \includegraphics[height=\flowh]{resources/Fig_Flows/1}
    \includegraphics[height=\flowh]{resources/Fig_Flows/2}
    \includegraphics[height=\flowh]{resources/Fig_Flows/3}
    \includegraphics[height=\flowh]{resources/Fig_Flows/4}
    \includegraphics[height=\flowh]{resources/Fig_Flows/5}
    \includegraphics[height=\flowh]{resources/Fig_Flows/6}
    \caption{Exemplar deformation fields for the left forearm, obtained using the proposed pipeline. Figure best viewed by zooming in.}
    \label{fig:deformationfield}
\end{figure}
